```{python echo=FALSE}
import python.api_calls as api
import pandas as pd
import warnings

warnings.filterwarnings('ignore')
```
```{r setup, include=FALSE}
#| echo: false
#| warning: false

library(reticulate)
api <- import("python.api_calls")
gain <- api$gain

source("Rscripts/table_formatting.R")

```

# Barrier Prioritization {-}


## Horsefly River Watershed Barrier Prioritization Summary {-}

The primary conservation outcome of the WCRP will be the remediation of barriers to connectivity in the Horsefly River watershed. To achieve Goal 1 in this plan, it is necessary to prioritize and identify a suite of barriers that, if remediated, will provide access to a minimum of `r gain` km of spawning or rearing habitat (@tbl-table16):


```{python echo=FALSE}
#| label: tbl-table16
#| tbl-cap: "Spawning and rearing habitat connectivity gain requirements to meet WCRP goals in the Horsefly River watershed. The measures of currently accessible and total habitat values are derived from the Intrinsic Potential habitat model described in Appendix B."
#| warning: false
#| echo: false

# Variables to API calls
connect = api.watershed_connectivity("ALL")[0]
total = round(api.watershed_connectivity("ALL")[1],2) #total km in HORS
access = round(api.watershed_connectivity("ALL")[2],2)
gain = round((total*0.96)-access,2)

# Data frame with table info
df = pd.DataFrame({"Habitat Type":["Spawning and Rearing"],
                   "Currently accessible (km)":[str(access)],
                   "Total": [str(total)],
                   "Current Connectivity Status":[str(connect)+"%"],
                   "Goal": ["96%"],
                   "Gain required (km)": [str(gain)]
                   })
                   
# Apply table styling
styled_df = df.style.hide().set_properties(**{'text-align': 'left'})
# header styling
table_styles = [{
       'selector': 'th',
       'props': [('background-color', '#008270'),('text-align', 'left')]
   }]
styled_df.set_table_styles(table_styles)

```

The barrier prioritization analysis ranked barriers by the amount of habitat blocked to produce an "intermediate barrier list" comprising more barriers than are needed to achieve the goals. A longer list of barriers is needed due to the inherent assumptions in the connectivity model, habitat model, and gaps in available data. Barriers that have been modelled (i.e., points where streams and road/rail networks intersect) are assumed to be barriers until field verification is undertaken and structures that have been assessed as "potential" barriers (e.g., may be passable at certain flow levels or for certain life history stages) require further investigation before a definitive remediation decision is made. Additionally, the habitat model identifies stream segments that have the potential to support spawning or rearing habitat for target species but does not attempt to quantify habitat quality or suitability (see Appendix B), which will require additional field verification once barrier assessments have completed. As such, the intermediate list of barriers below (@tbl-deficient) should be considered as a starting point in the prioritization process and represents structures that are a priority to evaluate further through barrier assessment and habitat confirmations because some structures will likely be passable, others will not be associated with usable habitat, and others may not be feasible to remediate because of logistic considerations. The intermediate barrier list was updated following the barrier assessments and habitat confirmations that were undertaken during the 2021 field season - some barriers were moved forward to the "priority barrier list" (see @tbl-priority) and others were eliminated from consideration due to one or more of the considerations discussed above (see @tbl-remove). The priority barrier list represents structures that were confirmed to be partial or full barriers to fish passage and that block access to confirmed habitat. Barriers on the priority list were reviewed by planning team members and selected for inclusion for proactive pursual of remediation.  For more details on the barrier prioritization model, please see @Mazany-Wright2021-rz.


```{r priority, echo = FALSE, results = 'asis'}
#| label: tbl-priority
#| tbl-cap: "The Horsefly River watershed priority barrier list, which includes barriers that have undergone field assessment, been reviewed by the planning team, and selected to pursue for proactive remediation."
#| warning: false
#| echo: false

data <- read.csv("data/priority_barriers_for_rehabilitation_table.csv", check.names=FALSE)
prior_num <- nrow(data)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r deficient, echo = FALSE, results = 'asis'}
#| label: tbl-deficient
#| tbl-cap: "Assessed structures that remain data deficient"
#| warning: false
#| echo: false

data <- read.csv("data/assessed_data_deficient_structures_table.csv", check.names=FALSE)
inter_num <- nrow(data)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```

```{r remove, echo = FALSE, results = 'asis'}
#| label: tbl-remove
#| tbl-cap: "List of barriers that were prioritized as part of the first iteration of the intermediate barrier list (field assessments occurred during the 2021 field season) but were removed from consideration for pursual of proactive remediation following discussion with the planning team due to these structures not existing, being passable, not be associated with usable habitat, or deemed not feasible to remediate because of logistic considerations."
#| warning: false
#| echo: false


data <- read.csv("data/excluded_structures_table.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```


Out of the `r inter_num` on the intermediate list, 16 require further field assessment before selection as a final barrier to pursue for remediation: 


There are currently `r prior_num` barriers on the priority barrier list, which will be pursued for proactive remediation to achieve the connectivity goals in this plan:


```{r rehab, echo = FALSE, results = 'asis'}
#| label: tbl-rehab
#| tbl-cap: "Rehabilitated structures."
#| warning: false
#| echo: false

data <- read.csv("data/rehabilitated_structures_table.csv", check.names=FALSE)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```