```{python echo=FALSE}
import python.api_calls as api
import pandas as pd
import warnings

warnings.filterwarnings('ignore')
```

```{r setup, include=FALSE}
#| echo: false
#| warning: false

library(reticulate)
api <- import("python.api_calls")
gain <- api$gain

source("Rscripts/table_formatting.R")

```

# Structure Prioritization {-}

## Structure Prioritization Summary {-}

A primary outcome of the WCRP is addressing barriers (i.e., removing or replacing the barrier, or temporarily adding a fish passage structure) to restore connectivity within the seven watersheds. To achieve the goals in this plan (@tbl-keas), it is necessary to identify a suite of barriers that, if addressed, will provide the largest, most important contribution towards restored connectivity of salmon and eel habitat. The following section outlines the ranking process to identify the list of barriers. 

After all existing data and knowledge are collated for known and modelled crossings, an iterative ranking process is conducted to help confirm barriers to target for rehabilitation to meet the goals. The ranking process is primarily used to guide field assessments and maximize efficiency in ground truthing data/knowledge inputs and model outputs, while providing a secondary purpose to evaluate the relative key habitat gains of confirmed barriers in the watershed. This process, combined with input from local knowledge holders and experts, is used to develop field plans for assessing structures that have the potential to block the most key habitat in the watershed.  

Field assessments can include an assessment of either the passability status of a structure (whether fish can pass upstream, and to what degree), whether the upstream habitat is suitable for the focal species, and whether there are other undocumented human-made or natural barriers upstream or downstream.

The ranking process accounts for long-term and immediate potential habitat gains offered by each structure to improve key habitat connectivity in the watershed. All structures in the watershed (excluding those confirmed as passage) were ranked and a subset of those structures were selected by the planning team to assess during the 2024 field season. Details of the ranking process used to guide field assessments can be found in ([Appendix C](defining-sets.qmd)) .

## Structure Prioritization Results {-}

Following field assessments, structures are placed on one of five possible lists:  

1. **Priority barriers list** – the structure is confirmed as 0, 25, 50, or 75% passable, has key habitat confirmed to exist upstream, and is considered actionable by the planning team (i.e., action items will be identified to address passability of the barrier). Depending on the barrier, owner, financial constraints, and quality of upstream habitat, the action may be to leave to end of life cycle before reviewing again, remove and decommission the road, replace with a new passable structure, or modify to temporarily restore connectivity (e.g., fish ladder or baffles installed; (@tbl-priority-as/@tbl-priority-ae/@tbl-priority-sm)). 

2. **Assessed structures that remain data deficient list** – some form of field assessment has been completed on the structure, but further investigation is required to confirm either the passability status or upstream habitat (@tbl-deficient). 

3. **Rehabilitated barriers list** – priority barriers that have been addressed (either through removal, replacement, or temporary fish passage improvement projects.  

4. **Non-actionable barriers list** – the structure is confirmed to be a barrier to fish passage and have some amount/quality of habitat upstream, but the planning team will not identify actions to address passability of the barrier because of logistic considerations (e.g., financial costs), short habitat gain, or the upstream habitat is of poor quality or unsuitable in its present condition to support key life stages of the focal species. 

5. **Excluded structures list** – the structure is excluded from further consideration in subsequent ranking and work planning because the structure is confirmed passable (e.g., bridge), not present, or there is no key habitat upstream ([Appendix D](additional-wcrp-tables.qmd)).  

```{r priority, echo = FALSE, results = 'asis'}
#| label: tbl-priority-as
#| tbl-cap: "The priority barrier list for Atlantic Salmon, which includes barriers that have undergone field assessment, been reviewed by the planning team, and selected to be addressed (whether removed, replaced with a passable structure, or provided temporary fish passage)."
#| warning: false
#| echo: false

data <- read.csv("data/priority-barriers-as.csv", check.names=FALSE)
prior_num <- nrow(data)
ft <- create_sorted_flextable(data)
ft <- format_flextable(ft)
ft
```

```{r priority, echo = FALSE, results = 'asis'}
#| label: tbl-priority-ae
#| tbl-cap: "The priority barrier list for American Eel, which includes barriers that have undergone field assessment, been reviewed by the planning team, and selected to be addressed (whether removed, replaced with a passable structure, or provided temporary fish passage)."
#| warning: false
#| echo: false

data <- read.csv("data/priority-barriers-ae.csv", check.names=FALSE)
prior_num <- nrow(data)
ft <- create_sorted_flextable(data)
ft <- format_flextable(ft)
ft
```

```{r priority, echo = FALSE, results = 'asis'}
#| label: tbl-priority-sm
#| tbl-cap: "The priority barrier list for Ranibow Smelt, which includes barriers that have undergone field assessment, been reviewed by the planning team, and selected to be addressed (whether removed, replaced with a passable structure, or provided temporary fish passage)."
#| warning: false
#| echo: false

data <- read.csv("data/priority-barriers-sm.csv", check.names=FALSE)
prior_num <- nrow(data)
ft <- create_sorted_flextable(data)
ft <- format_flextable(ft)
ft
```

```{r defic, echo = FALSE, results = 'asis'}
#| label: tbl-deficient
#| tbl-cap: "Assessed structures that remain data deficient"
#| warning: false
#| echo: false

data <- read.csv("data/assessed_data_deficient_structures_table.csv", check.names=FALSE)
prior_num <- nrow(data)
ft <- flextable(data)
ft <- format_flextable(ft)
ft
```
